### 2015-09-24 manuscript.Rnw
attempt at technical details section

Use NCL/\texttt{rncl} to parse NEXUS/Newick files.

Taxonomic information, singletons, but NCL can parse it.

@@

@@

>>>>

Phylogenetic information retrieved from OTL is converted into
\texttt{ape::phylo} objects by \texttt{rotl} using the NEXUS Class Library
\citep[NCL,][]{Lewis2003} as implemented in the \texttt{rncl} package
\url{https://cran.r-project.org/package=rncl}. Using NCL provides efficient
parsing of large trees that may contain singletons nodes labeled with taxonomic
information.

@@

Requesting a topology from a list of taxa takes place in two steps: the taxa
need to be matched to their identifiers in the Open Tree Taxonomy before
requesting the relationships among them. The first step is performed using the
TNRS.

@@

<<>>=
tt <- studies_find_studies(property = "ot:focalCladeOTTTaxonName", "mammalia")
@
